---
title: "Scrap Discuss HK"
author: "Paine (HE Peiwei, 54471952)"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
First, read the URL by using rvest, and the encoding is GBK. "Utf-8" is for OS system, but for Windows, the text should be encode in GBK.
```{r, eval=FALSE}
library(httr)
library(rvest)
url = "http://www.discuss.com.hk/viewthread.php?tid=26488701"
r = GET(url)
text = iconv(list(r$content), from="big5", to="GBK", sub="")
page = read_html(text)
```

Second, get comments to this post by using the html node, and check the css. 
```{r, eval=FALSE}
posts = page %>% html_nodes(".viewthread")

contents = posts %>% 
  html_node("span[id*='postorig']") %>% 
  html_text %>% trimws
```
Third, save the content's text to txt file.
```{r, eval=FALSE}
write.table(contents, file = "disshk.txt", sep = ",", col.names = colnames(alltext))
```

Fourth, get segment the Chinese text and calculate the frequency. And convert the frequency into dataframe.
```{r}
library(rJava)
library(Rwordseg)
library(wordcloud2)
text=segmentCN("disshk.txt",returnType = "tm")
text1=readLines("disshk.segment.txt", encoding = "UTF-8")
word = lapply(X = text1, FUN = strsplit, "\\s")
word1=unlist(word)
df=table(word1)
df=sort(df, decreasing = T)

d=data.frame(df)
newd = head(d, n=100)
newd<-newd[-1,]
head(newd)
```

Finally, output a wordcloud.
```{r}
library(wordcloud2)
wordcloud2(newd, color = "random-light", backgroundColor = "white")
```

```{r,echo=FALSE, eval=FALSE}
results = list()
while (TRUE) {
  url = "http://www.discuss.com.hk/viewthread.php?tid=26488701"
  r = GET(url)
  text = iconv(list(r$content), from="big5", to="GBK", sub="")
  page = read_html(text)
  posts = page %>% html_nodes(".viewthread")
  contents = posts %>% 
    html_node("span[id*='postorig']") %>% 
    html_text %>% trimws
  results[[url]] = contents
  # get next
  url = page %>% 
    html_node(".pages .next") %>% 
    html_attr("href")
  if (is.na(url)) break
  url = paste0("http://news.discuss.com.hk/", url, encoding="GBK")
}
# combine results
unlist(results, use.names = F)
```


```{r, echo=FALSE, eval=FALSE}
posts = page %>% html_nodes(".viewthread")

authors = posts %>% 
  html_nodes(".postauthor cite") %>% 
  html_text %>% trimws

posts
```

